\documentclass[11pt]{article}
\usepackage[top=2cm]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{setspace} 

\usepackage{helvet}
\usepackage{nopageno}

%\usepackage[german]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}


\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{History Homework on Churchill's Iron Curtain speech}
\author{Leon Handreke}
\date{}                                           % Activate to display a given date or no date

\begin{document}
\doublespacing
\maketitle
\fontfamily{phv}\selectfont

Kennan's assessment of Stalin's response to Churchill's speech in my opinion is in many parts right, although a strong bias towards western policies can be observed. His first point is that Stalin does not target the core statements of Churchill's speech but rather misinterprets some of the statements to make the response more appealing for ``home consumption''. In my opinion, this analysis is correct. Stalin says that Churchill considers the English speaking nations as superior, which is not the case. He also does not directly respond to the claim that Moscow is controlling the Eastern European states but speaks of the ``growth of the influence of communism'', citing failed western policies (``fascist regimes'') as the main reason for this. 

However, Kennan also claims that Churchill's statements were ``defensive in character'' and characterises Stalin's response as a ``violent reaction''. Looking at the document this is clearly not the case. Churchill directly attacks Stalin (``are seeking everywhere to obtain totalitarian control''). Stalin's response is equally aggressive, which seems to surprise Kennan (``most violent Soviet reaction I can recall'').

I think that the third point in the document is correct. I think that in the time after World War II, convincing as many people as possible of their ideology was equally important for both communists and capitalists. It comes to no surprise that Stalin uses mass media like newspapers to present his interpretation of Churchill's speech before they do themselves.

\end{document}  
