\documentclass[10pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or ...
\usepackage{setspace}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

\usepackage{helvet}
\usepackage{nopageno}

%\usepackage[german]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\title{Informal Email - Hang-gliding}
\author{Leon Handreke}
\date{}                                           % Activate to display a given date or no date

\begin{document}

\onehalfspacing

\maketitle
\fontfamily{phv}\selectfont

\textbf{To:} john.smith@failmail.com

\textbf{From:} leon.handreke@gmail.com

\textbf{Subject:} Summer holidays

Dear John,

we were talking about spending some time together next summer holidays last Friday and got stuck on ``some sort of flying activity''. I researched a little and found a school quite close to where I live that gives hang-gliding courses. It's not exactly as exciting as sky-diving or flying a real airplane, but their website has some photos on it and it looks like a lot of fun.

They offer a ``Discovery Flight'' with a professional instructor. The flight itself is about 20 minutes long, which makes it better value than a base-jump which is only about 3 minutes... They will even take a photo of you in flight for free!

The school itself looks very professional, it looks like they have perfect conditions for hand-gliding beginners: A long slope, a steep cliff about 800m high and many experienced instructors. They have been in the hang-gliding business since 1978, so they have a lot of experience when it comes to training new flyers They even have a campsite just by their landing zone, so we wouldn't have to go through the trouble of finding a hotel.

Of course all of this doesn't exactly come cheap; A single tandem flight is 129\$ and a ``Weekend Package'' (whatever that means) is 399\$. Nevertheless, I think it would be a great experience and great fun for both of us. And afterwards we can show off the photos of us flying to all of our friends!

I'd really like to hear what you think about this idea.

Hoping to hear from you soon,

Leon

\end{document}
