\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{a4paper}                   % ... or a4paper or a5paper or ...
\usepackage{setspace}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

\usepackage{helvet}
\usepackage{nopageno}

%\usepackage[german]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Graduation Speech}
\author{Leon Handreke}
\date{}                                           % Activate to display a given date or no date

\begin{document}

\onehalfspacing

\maketitle
\fontfamily{phv}\selectfont

Dear teachers, dear parents, and most importantly, dear students,

today we have come together for what may be the last time for many. Today is baccalaureate day. For the last time we will walk out of the school doors, say goodbye to our friends and close our lockers. Now being the end of so many things that we knew, it may seem like the end of everything. But today I do not want to talk about ends but about beginnings. We must always remind ourselves that every end can be a new beginning, a new opportunity awaiting us.

Think about the obvious opportunities: Most of us will be going to university next year. For most, it will be a totally new environment, both socially and physically. New people, a new city, maybe even a new country. Everything that was there before is now in the past. But being able to start over, and to begin anew is an incredible opportunity that we might not get very often in life.

But also think about the less obvious opportunities that we may be giving to other people. We are giving our friends and future friends we may not have met yet an opportunity to create new friendships for life. A new social environment is always difficult at first - but at the same time a great opportunity.

Next year, a new generation of students will come after us and have the opportunity to live through the same experiences as we have. As we are today, they will be standing here in one year, ready to leave, giving other students an opportunity to succeed them.

As you can see, we live in a world of opportunities. I hope that we will all be able to profit from the opportunities this day gives us. I congratulate all of you and wish you all the best for your future!

\end{document}
