\documentclass{letter}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage{setspace}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage{helvet}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\parindent 1cm

\address{Reverend Hale \\
Barn Street 3 \\
90210 Salem}
\signature{Reverend Hale}
\begin{document}
\onehalfspacing
\fontfamily{phv}\selectfont

\begin{letter}{Mr. Canon Westcliffe \\
Wizard Street 15 \\
59100 Boston}

\opening{Dear Mr. Westcliffe,}

I am writing to you to report about my recent findings in the village of Salem where I arrived yesterday. The village is in total shock at the moment, following a rumor of several women having compacted with the devil. Furthermore, unconfirmed claims of several girls having danced in the forest together and possibly engaged in witchcraft are circulating.

We are currently questioning a girl named Tituba, who claims to have been an honest and faithful individual since she arrived from Barbados several years ago . I am still validating the truth of this statement, but given that there is strong evidence of her having compacted with the devil and having gathered new souls since, I believe that she currently does not want to disclose her true intentions.

One major problem that the village is facing is that the local pastor, Reverend Parris, is no longer being trusted by most people in the village. The fact that his daughter is said to have participated in the dancing, lead by Tituba, puts his competence into question. This is why I kindly ask you to permit me to stay in Salem longer. I think that the people truly faithful to god in Salem need a strong leader more than ever. I think I can provide them with the expertise in witch hunting that is needed in such difficult times. I am hoping to set up a special court to completely drive the devil out of Salem. I hope that you will permit me to stay for another two weeks to rebuild he empire of the lord to remain stronger than ever.

\closing{Yours sincerely,}
\end{letter}

\end{document} 

