\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage{setspace}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

\usepackage{helvet}
\usepackage{nopageno}

%\usepackage[german]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}


\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Heat and Dust - Newspaper article about the narrator's pregnancy}
\author{Leon Handreke}
\date{}                                           % Activate to display a given date or no date

\begin{document}

%double line spacing
\doublespacing

\maketitle
\fontfamily{phv}\selectfont

A report from our correspondent in India indicates that a British woman currently living in the Satipur region of India is pregnant and scheduled to deliver towards the end of this year.  Upon speaking with her by telephone, we discovered that her child most likely has an Indian father. Upon further investigation we discovered that the father is Inder Lal, one of her neighbors and the renter of the room that she occupies at the moment.  They have been know to each other for about four months and have been engaged in an active relationship for about two months. We have also heard form various sources that the woman previously had a relationship with a British citizen she met in India. However, we believe it unlikely that he is the father given the time that has passed since her relationship with him and her own statement.

Another thing that we have discovered in our investigations is that the possible father of the child, Inder Lal is married to Ritu. However, as she is currently traveling in another part of the country, she was not available for us to comment on this issue.

\end{document} 

