\documentclass[10pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage{setspace}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

\usepackage{helvet}
\usepackage{nopageno}

%\usepackage[german]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}


\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Olivia's Diary - Arriving in India}
\author{Leon Handreke}
\date{}                                           % Activate to display a given date or no date

\begin{document}

%double line spacing
\doublespacing

\maketitle
\fontfamily{phv}\selectfont

We arrived in Satipur yesterday. I was glad to be able to leave the ferry as it got less comfortable in the small room on the boat the further we went south. A servant of the british ambassador fetched us from the quai in his car and we had a 5 hour drive to Satipur. The further we drove away from the coast, the more this country seemed like a desert to me.

This morining Mrs. Minnie and Mrs. Crawford came to visit me. They both friendly, but I noticed that they were somewhat reserved, almost unaware from the real world around them. It is probably the heat and the poverty around them that made them unemotional, almost disconnected from the natives.

Yesterday Douglas also had is first day at work. He now works in the administration and has to do with the natives a lot. He did not tell me a lot but Mrs. Minnie explained to me that he will usually have to do with the smaller quarrels in the Indian socienty. I am thinking that this may be the reason why he keeps our house locked up so tightly all the time. When I got up yesterday morning, he was already gone. This evening I asked Douglas if I could go to the bazaar tomorrow, but he said that it was too dangerous for me to go alone. I hope I will be able to convince him that we can go together on the weekend. I just hope the Crawfords are not going to invite us because I just don't want to stay in this artificial world of luxury and safety any longer. I want to go out, see the real India, however dusty, hot and dangerous it may be.

\end{document} 

