\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage{setspace}
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}

\usepackage{helvet}
\usepackage{nopageno}

%\usepackage[german]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}


\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\title{Personal Statement}
\author{Leon Handreke}
\date{}                                           % Activate to display a given date or no date

\begin{document}

%double line spacing
\doublespacing

\maketitle
\fontfamily{phv}\selectfont

\paragraph{}
From an early age I've always been deeply interested in computing and technology in general. It was my families first computer that sparked this interest. Since then I have always been interested in how computers and especially the software running on them worked.
\paragraph{}
The subjects I chose to study have partly helped me to develop both myself and my understanding of the subject. Physics for example has helped me to understand how certain parts of a computer function, while Maths has given me a solid basis to make sense of the more theoretical parts of computer science, such as cryptography.
\paragraph{}
My interest in computing has not been restricted to the classroom and college life. Within the last twelve months I've used the knowledge that I've gained over the past twelve years together to set up my own software development related business. This has given me a totally new perspective on how certain things function, and how business operates. Through the setting up of the company and its subsequent running I have learnt many things. These include how to balance tasks effectively, how critical teamwork can be and how to delegate tasks to get the job done quickly and efficiently. I have also learnt about many new aspects of software development and have gathered experience in how to write solid and elegant code.
\paragraph{}
As well as spending time both studying and helping to run the business I understand the importance of having time to relax. The hobbies that I try to make time for are airplanes and cycling. My fascination for airplanes has been going on for as long as I can remember. Nearly every week I visit the active runway at my local airport to look at the planes landing there. Also, I like doing bike tours on the weekends as a way of relaxing from the week's stress.
\paragraph{}
Having studied English for over 10 years, I am beginning to use it more than my mother tongue, German. Therefore I think I will not face any major problems studying at an English university.
\paragraph{}
Considering these factors it has never been out of question for me what to study once I would be finished with school. I am looking forward with great anticipation to the challenges that studying for a degree in computer science will bring.

\end{document}  
